Generating the Blueprints of the Java Ecosystem

### 2015-02-25 msr.tex
reading/writing stuff

% dimitro@bkarak: This section *does not* present the dataset. It presents Maven. You should rename the section to "Dataset Construction Process" and merge it with the upcoming one. It should go like this: 1) We got this snapshot and 2) applied these three tools to create what you see in the next section. You'll present the experiment and *advertise* the effort.

@@

The Java platform exists for more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications. The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}. The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as Java Specification Requests ({\sc jsr}s), which are supported by prototype implementations.

In the literature, it is suggested that {\sc dsl}s are used to reduce software development cost, by introducing domain efficiency \cite{MHS05}. This thesis focuses on practical research aspects as well as with the theoretical ones; thus the first problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects. In addition, the average number of {\sc dsl}s usually used in a software project needs to be investigated.

>>>>

@@

The Java platform exists for more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications. The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}.

By using the dataset, one small problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects. In addition, the average number of {\sc dsl}s usually used in a software project needs to be investigated.
